On the eletrodynamic of moving bodies

### 2019-05-29 Article_AS.Rmd
Fix wording

During the first half of the 20th century, most studies about genetic selection were dedicated on increasing wood volume production [@Dhir1976; @nienstaedt1985; @Li1997; @Koubaa2000] but with the increasing demand of high structural quality products and the fear of lossing ressource from natural causes, the aspects of wood quality became as important as wood volume [@Franceschini2012]. Therefore, conifer breeding programs are more and more considering wood quality as selection criteria to improve end-use properties. Wood quality has mainly two components: biologic and economic. The biologic component is the resistance to mortality by vigor and the economic component is the value of the wood for end-use. Several traits were considered for wood quality economic and the density is one of the most widely used indicators and arguably the most important one [@zobel1989; @Saranpaa1994; @Mckendry2002; @Macdonald2002; @Alteyrac2006] because this trait is important for both components of quality and strongly correlated with different mechanical (mechanical resistance and the dimensional stability) and anatomical wood traits [@zobel1989]. Thus, variation in density within a piece of wood may lead to deformation during transformation and inhomogeneous machining properties. Consequently studies have been set up to understand the genetic sources of phenotypic variations of wood quality [@Corriveau1971; @Li1993; @Hernandez2001; @Beaulieu2003; @Lenz2013; @McLean2016]. For example, future genetic selections in breeding programs for different species of spruce trees in Quebec will consider wood properties such as wood density [@Mullin2011; @Beaulieu2009]. 
With regard to the biological component, in has been demonstrated [@Hietz2013; @osazuwa2014] that trees with a more uniform wood densitiy within the stem are also the more resistant to mortality. For example a uniform density gives a greater mechanical resistance to the wind and therefore a lower probability of mortality during a climatic event such as a storm. With regard to the economical context, uniformity affects the performance of saw timber, the pulp yield and calorific values for biomass applications for bioenergy [@Hernandez2001; @Macdonald2002; @Mckendry2002]. For exemple, a strong interannual variation of the density of the wood leads to a decrease of the mechanical resistance while a relatively uniform density produce wood with better mechanical performance. It is therefore important from both a biological point of view and a end-use point of view to have a wood with a uniform density within the stem. \

>>>>

During the first half of the 20th century, most studies about genetic selection were dedicated on increasing wood volume production [@Dhir1976; @nienstaedt1985; @Li1997; @Koubaa2000] but with the increasing demand of high structural quality products and the fear of lossing ressource from natural causes, the aspects of wood quality became as important as wood volume [@Franceschini2012]. Therefore, conifer breeding programs are more and more considering wood quality as selection criteria to improve end-use properties. Wood quality has mainly two components: biologic and economic. The biologic component is the resistance to mortality by vigor and the economic component is the value of the wood for end-use. Several traits were considered to assess wood quality and the density is one of the most widely used indicators and arguably the most important one [@zobel1989; @Saranpaa1994; @Mckendry2002; @Macdonald2002; @Alteyrac2006]. Indeed this trait is important for both components of quality because it is strongly correlated with different mechanical and anatomical wood traits [@zobel1989]. Variation in density within a piece of wood may lead to deformation during transformation and inhomogeneous machining properties. Consequently studies have been set up to understand the genetic sources of phenotypic variations of wood quality [@Corriveau1971; @Li1993; @Hernandez2001; @Beaulieu2003; @Lenz2013; @McLean2016]. For example, future genetic selections in breeding programs for different species of spruce trees in Quebec will consider wood properties such as wood density [@Mullin2011; @Beaulieu2009]. 
With regard to the biological component, in has been demonstrated [@Hietz2013; @osazuwa2014] that trees with a more uniform wood densitiy within the stem are also the more resistant to mortality. For example a uniform density gives a greater mechanical resistance to the wind and therefore a lower probability of mortality during a climatic event such as a storm. With regard to the economical context, uniformity affects the performance of saw timber, the pulp yield and calorific values for biomass applications for bioenergy [@Hernandez2001; @Macdonald2002; @Mckendry2002]. For exemple, a strong interannual variation of the density of the wood leads to a decrease of the mechanical resistance while a relatively uniform density produce wood with better mechanical performance. It is therefore important from both a biological point of view and a end-use point of view to have a wood with a uniform density within the stem. \
